Standalone Tactics using OpenTheory

### 2011-10-20 paper.tex
Weber and Amjad as an example of multiple integrations

\section{Introduction}
There are many systems for interactively developing machine-checked formal theories, including HOL4~\cite{slind08brief}, HOL Light~\cite{DBLP:conf/tphol/Harrison09a}, ProofPower~\cite{ProofPower}, Isabelle/HOL~\cite{wenzel08isabelle}, and Coq~\cite{bertot08short}.
%All but the last are based on higher-order logic~\cite{church40formulation,gordon94hol} and follow the LCF tradition~\cite{gordon79lcf} wherein theorems are represented by an abstract datatype all of whose constructors, representing inference rules, are contained in a small, trusted kernel.
%In LCF-style provers, powerful proof procedures are kept trustworthy by, ultimately, only calling kernel functions to create theorems.
The logic implemented by these systems (except Coq) is essentially the same, but the collections of libraries and tactics built atop the logical kernels differ.
Where similar functionality exists in two systems it is usually the result of duplicate effort.
For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher order logic based system (HOL4 in one case and HOL Light in the other).

@@

>>>>

\section{Introduction}
There are many systems for interactively developing machine-checked formal theories, including HOL4~\cite{slind08brief}, HOL Light~\cite{DBLP:conf/tphol/Harrison09a}, ProofPower~\cite{ProofPower}, Isabelle/HOL~\cite{wenzel08isabelle}, and Coq~\cite{bertot08short}.
%All but the last are based on higher-order logic~\cite{church40formulation,gordon94hol} and follow the LCF tradition~\cite{gordon79lcf} wherein theorems are represented by an abstract datatype all of whose constructors, representing inference rules, are contained in a small, trusted kernel.
%In LCF-style provers, powerful proof procedures are kept trustworthy by, ultimately, only calling kernel functions to create theorems.
The logic implemented by these systems (except Coq) is essentially the same, but the collections of libraries and tactics built atop the logical kernels differ.
Where similar functionality exists in two systems it is usually the result of duplicate effort.
For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.

@@

Highly customised tactics for a particular proof system might suffer performance hits if the factorisation through the OpenTheory kernel cannot be done efficiently.
By the same token, the article format might admit optimisation by restructuring low-level proofs, and such optimisers could be widely applied.
